---
title: "This or That?"
author: "Roberta Rocca"
date: "23/04/2018"
output:
  html_document:
    encoding: UTF-8
---

Analysis of data on crosslinguistic study on semantic preferences in demonstratives use.
Data preprocessing performed separately for each dataset.
Markdowns available in the **Preprocessing** subfolder.

Run:
Sys.setlocale(category = "LC_ALL", locale = "da_dk.utf-8")
Sys.setlocale(category = "LC_MESSAGES", locale = "da_dk.utf-8")
For a correct visualization of the Danish characters


### Settings
Set plot parameters and Danish encoding
``` {r SetPlot, message = FALSE, warning = FALSE, echo = FALSE}
library(sjPlot)
library(ggplot2)
library(cowplot)
library(ggrepel)

# Set plot parameters
set_theme(axis.textsize = 1,
          axis.title.size = 1, 
          title.size = 1, legend.size = 1, legend.title.size = 1, 
          theme.font = 'Times New Roman')

# Set Danish encoding
Sys.setlocale(category = "LC_ALL", locale = "da_dk.utf-8")
Sys.setlocale(category = "LC_MESSAGES", locale = "da_dk.utf-8")
```

### Analysis
Includes logistic regression using categorical predictors per each dataset, as well as cumulative analysis.
Also includes parametrized version using animacy, harmfulness and size scores.
Loading the dataset with information on experimental words
``` {r LoadAllData, message = FALSE, warning = FALSE}
library(readr)
library(lme4)
library(dplyr)

# Read in the dataframes with scores for experimental words along each dimension
exp1 <- read.table('exp1.txt', sep = '\t', header = TRUE)
exp2 <- read.table('exp2.txt', sep = '\t', header = TRUE)
exp1 <- exp1[, c(1:(ncol(exp1) - 3))]
exp2 <- exp2[, c(1:(ncol(exp2) - 3))]

head(exp1)
head(exp2)

```

Load the frequency data
``` {r LoadFreqData, message = FALSE, warning = FALSE}

# BNC
freq_bnc <- read_tsv('freq_bnc.txt')
# Danish
freq_dk <- read_tsv('freq_dk.txt')
freq_dk$Freq <- freq_dk$Freq / 2570.805
#Italian
freq_it <- read_tsv('freq_it.txt')
freq_it$Freq <- freq_it$Freq / 5864.496
# Merge all the frequency data in a single dataset.
freq <- rbind(freq_bnc[, 2:3], freq_dk)
freq <- rbind(freq, freq_it)

```

Read in the data from the experiment
**Please note** that there might be issues with the encoding of Danish characters. 
Check how they're read in, and change code accordingly.
``` {r ExpData, message = FALSE, warning = FALSE}

# Load experiment 1
data_EN <- read.table('EN_1.txt', sep = '\t', header = TRUE)
data_IT <- read.table('IT_1.txt', sep = '\t', header = TRUE)
data_DK <- read.table('DK_1.txt', sep = '\t', header = TRUE)

# Load experiment 2
data_IT2 <- read.table('IT_2.txt', sep = '\t', header = TRUE)
data_DK2 <- read.table('DK_2.txt', sep = '\t', header = TRUE)

# Replace misprinted Danish characters
data_DK$Noun <- plyr::mapvalues(data_DK$Noun, from=c('n.l', 'sm.kage', 'f.rekylling', 'g.s', 'hy.ne', 'f.ngsel', 'r.dhals', 's.be', 'b.nk', 'm.nt'), to=c('n??l', 'sm??kage', 'f??rekylling', 'g??s', 'hy??ne', 'f??ngsel', 'r??dhals', 's??be', 'b??nk', 'm??nt'))
data_DK2$Noun <- plyr::mapvalues(data_DK2$Noun, from=c('skovfl.t', 'r.dyr', 'egetr.', 'X.ble'),to=c('skovfl??t', 'r??dyr', 'egetr??', '??ble'))

# list of italian words for exp2
it_words_2 <- c('tigre', 'cobra', 'coccodrillo', 'cinghiale', 'zanzara', 'medusa', 'tarantola', 'zecca','giraffa', 'cavallo', 'delfino', 'cerbiatto', 'coniglio', 'farfalla', 'scoiattolo', 'passero','meteorite', 'valanga', 'vulcano', 'bombardiere', 'mina', 'veleno', 'proiettile', 'coltello','scuola', 'quercia', 'contrabbasso', 'cupola', 'tazza', 'scarpa', 'cucchiaio', 'mela')
# list of Danish words for exp2
dk_words_2 <- c('tiger', 'kobra', 'krokodille', 'vildsvin', 'myg', 'giftgople', 'fugleedderkop', 'skovfl??t','giraf', 'hest', 'delfin', 'r??dyr', 'kanin', 'sommerfugl', 'egern', 'spurv','meteor', 'lavine', 'vulkan', 'bombefly', 'landmine', 'gift', 'patron', 'kniv','skole', 'egetr??', 'kontrabas', 'kuppel', 'krus', 'sko', 'ske', '??ble')
# List of english words for exp 2

exp_words_2 <- c('tiger', 'cobra', 'crocodile', 'boar', 'mosquito', 'jellyfish', 'tarantula', 'tick','giraffe', 'horse', 'dolphin','fawn', 'rabbit', 'butterfly','squirrel', 'sparrow', 'meteorite', 'avalanche', 'volcano', 'bomber', 'landmine', 'poison', 'bullet', 'knife',
                 'school', 'oak', 'bass', 'dome', 'mug', 'shoe', 'spoon', 'apple')


# Replace nouns in IT ad DK with English equivalents
data_IT$NounEng <- plyr::mapvalues(data_IT$Noun, from=unique(as.character(data_IT$Noun)), to= unique(as.character(data_EN$Noun)))
data_DK$NounEng <- plyr::mapvalues(data_DK$Noun, from=unique(as.character(data_DK$Noun)), to=unique(as.character(data_EN$Noun)))

# Same for experiment 2
data_IT2$NounEng <- plyr::mapvalues(data_IT2$Noun, from=it_words_2, to = exp_words_2)
data_DK2$NounEng <- plyr::mapvalues(data_DK2$Noun, from=dk_words_2, to = exp_words_2)

# Add Lang info to the dataset (for merging)
data_IT$Lang <- 'IT'
data_DK$Lang <- 'DK'
data_EN$Lang <- 'EN'
data_IT2$Lang <- 'IT'
data_DK2$Lang <- 'DK'

# Rename
colnames(data_EN)[9] <- 'NounEng'
data_EN$Noun <- data_EN$NounEng

```

Including info on experimental variables and merging all in single dataset
``` {r MergeData, message = FALSE, warning = FALSE}

# Merge dataset from experiment 1 with scores and category
data_EN <- merge(data_EN, exp1, by.x = 'NounEng', by.y = 'Noun')
data_IT <-merge(data_IT, exp1, by.x = 'NounEng', by.y = 'Noun')
data_DK <-merge(data_DK, exp1, by.x = 'NounEng', by.y = 'Noun')

# Merge Danish and English data
data <- rbind(data_EN[, -c(7,8)], data_DK)
# Add a column which is there in the Italian dataset
data$Incorrect <- 'Correct'
# Merge with Italian
data <- rbind(data, data_IT[, -c(10)])
# Add info on number of experiment
data$ExpNr <- 1

# Now merge data for exp2
data_IT2 <-merge(data_IT2, exp2, by.x = 'NounEng', by.y = 'Noun')
data_DK2 <-merge(data_DK2, exp2, by.x = 'NounEng', by.y = 'Noun')
data2 <- rbind(data_IT2, data_DK2)
data2$ExpNr <- 2
data2$Incorrect <- 'Correct'

# Merge data from the two experiments
data_all <- rbind(data, data2)
data_all$Noun <- plyr::mapvalues(data_all$Noun, from=c('b??nk', 'm??nt', 'sm??kage', 'f??rekylling',  'g??s', 'hy??ne', 'f??ngsel', 'n??l', 'r??dhals', 's??be', '??ble', 'r??dyr', 'egetr??', 'skovfl??t'), to = c('bænk', 'mønt', 'småkage', 'fårekylling', 'gås', 'hyæne', 'fængsel', 'nål', 'rødhals', 'sæbe', 'æble', 'rådyr', 'egetræ', 'skovflåt'))
data_all <- merge(data_all, freq, by.x = 'Noun', by.y = 'Word')

# Check small error
data_all$Animate[data_all$NounEn %in% c('spider', 'kitten')] <- 'Animate'

# Just because it's handy: also keep a copy of separate datasets
data_IT <- subset(data_all, Lang == 'IT' & ExpNr == 1)
data_DK <- subset(data_all, Lang == 'DK' & ExpNr == 1)
data_EN <- subset(data_all, Lang == 'EN' & ExpNr == 1)
data_IT2 <- subset(data_all, Lang == 'IT' & ExpNr == 2)
data_DK2 <- subset(data_all, Lang == 'DK' & ExpNr == 2)

```


Proportion of proximal demonstratives across experimental variables for each of the languages and experiments
``` {r CumulativePlots, message = FALSE, warning = FALSE, echo = FALSE}

# Summarize the data by experimental variable for experiment 1
agg_cat <- data %>% group_by(Lang, Animate, Size, Harm, Demonstrative) %>% summarize(count = n()) %>% mutate(prop = count/sum(count)) %>% data.frame()
# Do the same for experiment 2
agg_cat2 <- data2 %>% group_by(Lang, Animate, Size, Harm, Demonstrative) %>% summarize(count = n()) %>% mutate(prop = count/sum(count)) %>% data.frame()
# Keep only info on proximal demonstratives
agg_cat <- subset(agg_cat, Demonstrative == 'proximal')
levels(agg_cat$Animate)[levels(agg_cat$Animate) == 'Non_Animate'] <- 'Inanimate'
agg_cat2 <- subset(agg_cat2, Demonstrative == 'proximal')
levels(agg_cat2$Animate)[levels(agg_cat2$Animate) == 'Non_Animate'] <- 'Inanimate'

# Special plot for Italian data from the first experiment: inspect effect of soundness of the demonstrative/noun match
it_cat <- subset(data, Lang == 'IT') %>% group_by(Incorrect, Size, Harm, Demonstrative) %>% summarize(count = n()) %>% mutate(prop = count/sum(count))
it_cat <- subset(it_cat, Demonstrative == 'proximal')

# Create plots
plot_CAT <- ggplot(data = subset(agg_cat)) + 
  geom_bar(aes(x = Harm, y = prop, fill = Size), stat = 'identity', position = 'dodge', alpha = 0.7) +
  facet_grid(Lang~Animate) + 
  geom_hline(yintercept = 0.5, linetype = 'dashed') +
  xlab('') + ylab('Proportion proximal demonstratives') + ggtitle('')+
  scale_fill_brewer(palette="Set1") + 
  
  theme(strip.text = element_text(size = 12), strip.background =element_rect(fill="white"), axis.title.y = element_text(size = 12),
        legend.text = element_text(size = 12), legend.title = element_text(size = 12)) +
  
  theme(panel.background = element_rect(fill='white', color = 'black'),
        panel.grid.major = element_line(color = 'grey', linetype = 'dotted'),
        panel.grid.minor = element_line(color = 'grey', linetype = 'dotted'))

plot2_CAT <- ggplot(data = subset(agg_cat2)) +
  geom_bar(aes(x = Harm, y = prop, fill = Size), stat = 'identity', position = 'dodge', alpha = 0.7) +
  facet_grid(Lang~Animate) + 
  geom_hline(yintercept = 0.5, linetype = 'dashed') +
  xlab('') + ylab('Proportion proximal demonstratives')+ ggtitle('')+
  scale_fill_brewer(palette="Set1")+ 
 
  theme(strip.text = element_text(size = 12), strip.background =element_rect(fill="white"), axis.title.y = element_text(size = 12),
        legend.text = element_text(size = 12), legend.title = element_text(size = 12)) +
  
  theme(panel.background = element_rect(fill='white', color = 'black'),
        panel.grid.major = element_line(color = 'grey', linetype = 'dotted'),
        panel.grid.minor = element_line(color = 'grey', linetype = 'dotted'))

plot_IT_cat <- ggplot(data = subset(it_cat)) +
  geom_bar(aes(x = Harm, y = prop, fill = Size), stat = 'identity', position = 'dodge', alpha = 0.7) +
  facet_wrap(~Incorrect) +
  geom_hline(yintercept = 0.5, linetype = 'dashed') +
  xlab('') + ylab('Proportion proximal demonstratives') +
  scale_fill_brewer(palette="Set1")+ 
   
  theme(strip.text = element_text(size = 12), strip.background =element_rect(fill="white"), axis.title.y = element_text(size = 12),
        legend.text = element_text(size = 12), legend.title = element_text(size = 12)) +
  
  theme(panel.background = element_rect(fill='white', color = 'black'),
        panel.grid.major = element_line(color = 'grey', linetype = 'dotted'),
        panel.grid.minor = element_line(color = 'grey', linetype = 'dotted'))


# Print out the plots
plot_CAT
plot2_CAT
plot_IT_cat

```

Stats: mixed-effects logistic regression for each of the experiments.
Same model used for all languages, fixed effects structure including all the experimental factors and full interaction structure.
Random effects structure include random intercept for ID.
More complicated random effects structure fitted in the overall model.

#### Experiment 1

``` {r StatsAll, message = FALSE, warning = FALSE}

# Model all data, add fixed effect of language and interactions
model_1 <- glmer(data = subset(data_all, !(ExpNr == 2)), 
                 factor(Demonstrative) ~ Animate * Size * Harm * Lang + (1|ID), 
                 family = 'binomial', 
                 glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))
summary(model_1)

```

Zoom: Italian data
``` {r StatsIta, message = FALSE, warning = FALSE}
it_log1 <- glmer(data = data_IT, 
                 factor(Demonstrative) ~ Animate * Size * Harm + (1|ID), 
                 family = 'binomial', 
                 glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))
summary(it_log1)
```

Compare previous model for Italian with one taking into account the soundness of the coupling between noun and distal demonstratives
``` {r StatsItaCorrect, message = FALSE, warning = FALSE}
 
it_corr <-glmer(data = data_IT, 
                factor(Demonstrative) ~ Animate * Size * Harm + Incorrect + Incorrect:Animate + Incorrect:Harm + Incorrect:Size + (1|ID), 
                family = 'binomial', 
                glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))

# Compare the model with the previous one
anova(it_log1, it_corr)

# Visualize result of the model
summary(it_corr)
```


Model for experiment 2
``` {r StatsAll2, message = FALSE, warning = FALSE}

# Model all data, add fixed effect of language and interactions
model_2 <- glmer(data = subset(data_all, !(ExpNr == 1)), 
                 factor(Demonstrative) ~ Animate * Size * Harm * Lang + (1|ID), 
                 family = 'binomial', 
                 glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))

summary(model_2)
```

### Overall analysis
Adding more complex random effects structure (exclude Italian data)
``` {r StatsAllRFX, message = FALSE, warning = FALSE}

model_rfx <- glmer(data = subset(data_all, !(Lang == 'IT' & ExpNr == 1)), 
                   factor(Demonstrative) ~ Animate * Size * Harm * Lang + (1|ID) + (1|Animate:NounEng) + (1|Size:NounEng) + (1|Harm:NounEng), 
                   family = 'binomial', 
                   glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))
summary(model_rfx)

```

#### Parametric version of the analysis
Here we look at whether the effects found in the logistic analysis are confirmed when using 1-5 scores for size and harmfulness.
Scores are taken from the Sudre et al. (2012) database for experiment one, whereas for experiment two, scores are predicted using SVR on GloVe word vectors to predict 1-5 scores. Models are tuned and trained on words from Sudre et al. (2012).
``` {r StatsParam, message = TRUE, warning = TRUE}

# All parametric model
all_par <- glmer(data = subset(data_all, !(ExpNr == 1 & Lang == 'IT')), 
                 Demonstrative ~ Animate + as.numeric(SizeScore) + as.numeric(HarmScore) + Animate:as.numeric(SizeScore) + Animate:as.numeric(HarmScore)+ (1|ID), 
                 family = 'binomial', 
                 glmerControl(optimizer="bobyqa", optCtrl = list(maxfun = 100000)))

summary(all_par)

```

### Frequency
Are there systematic differences in **frequency** between levels of our experimental variables, which might confound the results?
We looked up word frequencies in all of the language, plotted it and ran statistical tests.
First step: read in the frequency data for English: BNC data
Data extracted from <http://ucrel.lancs.ac.uk/bncfreq/>, updated to 2001. 
Values refer to rounded lemma frequency per million token.
``` {r ReadBNC, message = FALSE, warning = FALSE}
library(readr)

# Read in TSV with frequency data for all the words in the two experiments
freq_bnc <- read_tsv('freq_bnc.txt')

# Only keep relevant columns (i.e. delete empty index value)
freq_bnc <- freq_bnc[, 2:3]

# Add info on experimental categories 
freq_bnc$Animate <- c(1,0,0,1,0,1,0,0,0,0,0,1,0,1,1,1,0,1,1,0,1,1,0,1,0,1,1,1,0,1,0,0,0,0,0,1,0,0,1,1,1,1,0,1,1,1,1,0,0,0,1,0,0,0,1,0,0,1,0,1,1,1,1,0)

freq_bnc$Harm <- c(1,0,1,1,1,0,0,0,0,0,0,0,1,1,0,1,1,0,0,1,0,1,1,0,1,1,0,1,0,1,0,1,0,1,0,1,1,1,0,1,1,0,0,0,0,0,1,1,1,1,1,0,0,1,0,0,0,0,0,0,1,1,1,1)

freq_bnc$Size<- c(0,1,1,1,0,1,0,0,0,1,1,0,0,0,1,1,1,0,1,0,1,0,1,0,1,1,0,1,0,0,1,0,0,1,1,1,1,0,0,1,1,1,1,1,1,1,0,0,1,0,0,0,1,0,0,1,0,0,0,0,0,0,1,1)

# Recode to nicer category values
freq_bnc$Animate <- ifelse(freq_bnc$Animate == 1, 'Animate', 'Inanimate')
freq_bnc$Harm <- ifelse(freq_bnc$Harm == 1, 'Harmful', 'Harmless')
freq_bnc$Size <- ifelse(freq_bnc$Size == 1, 'Big', 'Small')

# Add info on which experiment each word belongs to
freq_bnc$Exp <- c(rep(1,32), rep(2,32))
head(freq_bnc)
```

Boxplots displaying frequencies by experimental factor for experiment one
``` {r FreqExp1, message = FALSE, warning = FALSE, echo = FALSE}

# By animacy
bnc_anim_1 <- ggplot(data = subset(freq_bnc, Exp == 1), aes(x = Animate, y = Freq)) +
  geom_boxplot(aes (fill = Animate), alpha = 0.7) +
  ylab('Frequency') + xlab('')  +
  guides(fill = FALSE) + # No legend
  geom_text_repel(aes(label = ifelse(Freq > 30, Word, ''))) + # Add labels for outliers
  scale_fill_brewer(palette="Set1") +
  theme(panel.background = element_rect(fill='white', color = 'black'),
        panel.grid.major = element_line(color = 'grey', linetype = 'dotted'),
        panel.grid.minor = element_line(color = 'grey', linetype = 'dotted'))

# By harm
bnc_harm_1 <- ggplot(data = subset(freq_bnc, Exp == 1), aes(x = Harm, y = Freq)) +
  geom_boxplot(aes (fill = Harm), alpha = 0.7) +
  ylab('') + xlab('')  +
  guides(fill = FALSE) +
  geom_text_repel(aes(label = ifelse(Freq > 35, Word, ''))) +
  scale_fill_brewer(palette="Set1") + 
  theme(plot.title = element_text(hjust = 0.5))+
  theme(panel.background = element_rect(fill='white', color = 'black'),
        panel.grid.major = element_line(color = 'grey', linetype = 'dotted'),
        panel.grid.minor = element_line(color = 'grey', linetype = 'dotted'))

# By size
bnc_size_1 <- ggplot(data = subset(freq_bnc, Exp == 1), aes(x = Size, y = Freq)) +
  geom_boxplot(aes (fill = Size), alpha = 0.7) +
  ylab('') + xlab('')  +
  guides(fill = FALSE) +
  geom_text_repel(aes(label = ifelse(Size == 'Big' & Freq > 25, Word, ''))) +
  scale_fill_brewer(palette="Set1")+
  theme(panel.background = element_rect(fill='white', color = 'black'),
        panel.grid.major = element_line(color = 'grey', linetype = 'dotted'),
        panel.grid.minor = element_line(color = 'grey', linetype = 'dotted'))

bnc_anim_1
bnc_harm_1
bnc_size_1

```

Boxplots for frequencies by experimental factor for experiment 2
``` {r Exp2, warning = FALSE, message = FALSE, echo = FALSE}

# By animacy
bnc_anim_2 <- ggplot(data = subset(freq_bnc, Exp == 2), aes(x = Animate, y = Freq)) +
  geom_boxplot(aes (fill = Animate), alpha = 0.7) + ylab('Frequency') + xlab('')  + guides(fill = FALSE)+
  geom_text_repel(aes(label = ifelse(Freq > 40, Word, ''))) +
  scale_fill_brewer(palette="Set1")+
  theme(panel.background = element_rect(fill='white', color = 'black'),
        panel.grid.major = element_line(color = 'grey', linetype = 'dotted'),
        panel.grid.minor = element_line(color = 'grey', linetype = 'dotted'))

# By harm 
bnc_harm_2 <- ggplot(data = subset(freq_bnc, Exp == 2), aes(x = Harm, y = Freq)) +
  geom_boxplot(aes (fill = Harm), alpha = 0.7) + ylab('') + xlab('')  + guides(fill = FALSE)+
  geom_text_repel(aes(label = ifelse(((Harm == 'Harmful' & Freq > 30) | (Harm == 'Harmless' & Freq > 100)), Word, ''))) +
  scale_fill_brewer(palette="Set1") +
  theme(plot.title = element_text(hjust = 0.5))+
  theme(panel.background = element_rect(fill='white', color = 'black'),
        panel.grid.major = element_line(color = 'grey', linetype = 'dotted'),
        panel.grid.minor = element_line(color = 'grey', linetype = 'dotted'))

# By size
bnc_size_2 <- ggplot(data = subset(freq_bnc, Exp == 2), aes(x = Size, y = Freq)) +
  geom_boxplot(aes (fill = Size), alpha = 0.7) + ylab('') + xlab('')  + guides(fill = FALSE) +
  geom_text_repel(aes(label = ifelse(Freq > 40, Word, ''))) +
  scale_fill_brewer(palette="Set1")+
  theme(panel.background = element_rect(fill='white', color = 'black'),
        panel.grid.major = element_line(color = 'grey', linetype = 'dotted'),
        panel.grid.minor = element_line(color = 'grey', linetype = 'dotted'))

bnc_anim_2
bnc_harm_2
bnc_size_2

```

Test if there any any significant differences in word frequency across the three categories (English)
Trying to rule out the possibility that any effect would be driven by word frequency
``` {r FreqModel, message = FALSE, warning = FALSE}
library(lme4)
library(lmerTest)
library(car)

# Fit linear model
bnc_lm <- lm(data = subset(freq_bnc, Exp == 1), Freq ~ Animate * Harm * Size)
bnc_lm2 <- lm(data = subset(freq_bnc, Exp == 2), Freq ~ Animate * Harm * Size)

# Look up summaries 
Anova(bnc_lm)
Anova(bnc_lm2)

```

There does not seem to be any significant difference. 
Let's run the same control tests for Danish. 
Frequencies here are drawn from the Danish web corpus daTenTen, version 2017. 
For info on these corpora see: <https://en.wikipedia.org/wiki/TenTen_Corpus_Family>.
Data have been downloaded via <https://www.sketchengine.eu>.
As for English, values stand for lemma frequency per million words.

``` {r ReadFreq, warning = FALSE, message = FALSE}

# Read in frequency file for Danish
freq_dk <- read_tsv('freq_dk.txt')

# Add experimental information on words (both experiments)
animals_dk=c('bi', 'lam', 'rødhals', 'fårekylling', 'gås', 'tyr', 'pingvin', 'haj', 'kamel',
             'hyæne', 'reje', 'edderkop','rotte', 'loppe', 'slange', 'killing','tiger',
             'kobra', 'krokodille', 'vildsvin', 'myg', 'giftgople', 'fugleedderkop', 'skovflåt', 'giraf',
             'hest', 'delfin', 'rådyr', 'kanin' ,'sommerfugl','egern','spurv')

big_dk=c('tyr', 'hyæne', 'slange', 'haj', 'kamel', 'gås', 'lam', 'pingvin',
         'bombe', 'fængsel', 'missil', 'riffel', 'bænk', 'sofa', 'vugge', 'telt',
         'meteor', 'lavine', 'vulkan', 'bombefly', 'tiger', 'kobra', 'krokodille', 'vildsvin',
         'giraf', 'hest', 'delfin', 'rådyr' ,'skole','egetræ','kontrabas','kuppel')

harmful_dk=c('tyr', 'hyæne', 'haj', 'slange', 'bi', 'loppe', 'edderkop', 'rotte',
             'bombe', 'fængsel', 'missil', 'riffel', 'blus', 'dolk', 'nål', 'torn',
             'tiger', 'kobra', 'krokodille','vildsvin','meteor', 'lavine', 'vulkan', 'bombefly',
             'myg', 'giftgople', 'fugleedderkop', 'skovflåt', 'landmine', 'gift', 'patron', 'kniv')

dk_words_2 <- c('tiger', 'kobra', 'krokodille', 'vildsvin', 'myg', 'giftgople', 'fugleedderkop', 'skovflåt',
                'giraf', 'hest', 'delfin', 'rådyr', 'kanin', 'sommerfugl', 'egern', 'spurv',
                'meteor', 'lavine', 'vulkan', 'bombefly', 'landmine', 'gift', 'patron', 'kniv',
                'skole', 'egetræ', 'kontrabas', 'kuppel', 'krus', 'sko', 'ske', 'æble')

# Add this info to the frequency dataset
freq_dk$Animate <- ifelse(freq_dk$Word %in% animals_dk, 'Animate', 'Inanimate')
freq_dk$Size <- ifelse(freq_dk$Word %in% big_dk, 'Big', 'Small')
freq_dk$Harm <- ifelse(freq_dk$Word %in% harmful_dk, 'Harmful', 'Harmless')
# Add info on experiment number
freq_dk$Exp <- ifelse(freq_dk$Word %in% dk_words_2, 2, 1)
# Rescale frequency per million words
freq_dk$PerMillion <- freq_dk$Freq / 2570.805 # Million words in the corpus

head(freq_dk)
```

Boxplot displaying frequency for **Danish** words, experiment 1
``` {r PlotFreqDK, message = FALSE, warning = FALSE, echo = FALSE}

# By animacy
dk_anim_1 <- ggplot(data = subset(freq_dk, Exp == 1), aes(x = Animate, y = PerMillion)) +
  geom_boxplot(aes (fill = Animate), alpha = 0.7) + ylab('Frequency') + xlab('')  + guides(fill = FALSE) +
  geom_text_repel(aes(label = ifelse(Animate == 'Animate' & PerMillion > 15, Word, ''))) +
  scale_fill_brewer(palette="Set1")+
  theme(panel.background = element_rect(fill='white', color = 'black'),
        panel.grid.major = element_line(color = 'grey', linetype = 'dotted'),
        panel.grid.minor = element_line(color = 'grey', linetype = 'dotted'))

# By harmfulness
dk_harm_1 <- ggplot(data = subset(freq_dk, Exp == 1), aes(x = Harm, y = PerMillion)) +
  geom_boxplot(aes (fill = Harm), alpha = 0.7) + ylab('') + xlab('')  + guides(fill = FALSE) +
  geom_text_repel(aes(label = ifelse(Freq > 60000, Word, ''))) +
  scale_fill_brewer(palette="Set1")+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(panel.background = element_rect(fill='white', color = 'black'),
        panel.grid.major = element_line(color = 'grey', linetype = 'dotted'),
        panel.grid.minor = element_line(color = 'grey', linetype = 'dotted'))

# By size
dk_size_1 <- ggplot(data = subset(freq_dk, Exp == 1), aes(x = Size, y = PerMillion)) +
  geom_boxplot(aes (fill = Size), alpha = 0.7, ) + ylab('') + xlab('')  + guides(fill = FALSE) +
  geom_text_repel(aes(label = ifelse(Size == 'Small' & Freq > 50000, Word, ''))) +
  scale_fill_brewer(palette="Set1") +
  theme(panel.background = element_rect(fill='white', color = 'black'),
        panel.grid.major = element_line(color = 'grey', linetype = 'dotted'),
        panel.grid.minor = element_line(color = 'grey', linetype = 'dotted'))

dk_anim_1
dk_harm_1
dk_size_1

```

Boxplot displaying word frequency distribution for experiment 2 (Danish)
``` {r PlotFreqDK2, message = FALSE, warning = FALSE, echo = FALSE}

# By animacy
dk_anim_2 <- ggplot(data = subset(freq_dk, Exp == 2), aes(x = Animate, y = PerMillion)) +
  geom_boxplot(aes (fill = Animate), alpha = 0.7) + ylab('Frequency') + xlab('')  + guides(fill = FALSE)+
  geom_text_repel(aes(label = ifelse(Animate == 'Animate' & PerMillion > 10 | Animate == 'Inanimate' & PerMillion > 50, Word, ''))) +
  scale_fill_brewer(palette="Set1")+
  theme(panel.background = element_rect(fill='white', color = 'black'),
        panel.grid.major = element_line(color = 'grey', linetype = 'dotted'),
        panel.grid.minor = element_line(color = 'grey', linetype = 'dotted'))

# By harmfulness
dk_harm_2 <- ggplot(data = subset(freq_dk, Exp == 2), aes(x = Harm, y = PerMillion)) +
  geom_boxplot(aes (fill = Harm), alpha = 0.7) + ylab('') + xlab('')  + guides(fill = FALSE) +
  geom_text_repel(aes(label = ifelse(((Harm == 'Harmful' & Freq > 30000) | (Harm == 'Harmless' & Freq > 125000)), Word, ''))) +
  scale_fill_brewer(palette="Set1")+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(panel.background = element_rect(fill='white', color = 'black'),
        panel.grid.major = element_line(color = 'grey', linetype = 'dotted'),
        panel.grid.minor = element_line(color = 'grey', linetype = 'dotted'))

# By size
dk_size_2 <- ggplot(data = subset(freq_dk, Exp == 2), aes(x = Size, y = PerMillion)) +
  geom_boxplot(aes (fill = Size), alpha = 0.7) + ylab('') + xlab('')  + guides(fill = FALSE)+
  geom_text_repel(aes(label = ifelse(Freq > 125000, Word, ''))) +
  scale_fill_brewer(palette="Set1")+
  theme(panel.background = element_rect(fill='white', color = 'black'),
        panel.grid.major = element_line(color = 'grey', linetype = 'dotted'),
        panel.grid.minor = element_line(color = 'grey', linetype = 'dotted'))

dk_anim_2
dk_harm_2
dk_size_2

```

Are there any significant differences in words frequency for Danish?
``` {r ModelFreqDK, message = FALSE, warning = FALSE}

# Run linear regression (same FFX structure as the analyis)
dk_lm1 <- lm(data = subset(freq_dk, Exp == 1), PerMillion ~ Animate * Harm * Size)
dk_lm2 <- lm(data = subset(freq_dk, Exp == 2), PerMillion ~ Animate * Harm * Size)

# Visualize results
Anova(dk_lm1)
Anova(dk_lm2)

```

Check word frequency for Italian
As for Danish, word frequencies were extracted from from the itTenTen corpus, version 2017, using <https://www.sketchengine.eu>.
Values denote lemma frequency per million words.
``` {r DataImport, message = FALSE, warning = FALSE}

# Read in the frequency dataframe
freq_it <- read_tsv('freq_it.txt')

# Add info on Animacy (looks clumsy but it is correct ;) )
freq_it$Animate <- c(1,0,0,0,0,0,0,1,0,0,1,0,0,0,1,1,1,0,1,1,0,1,1,0,1,1,1,1,0,0,1,1,0,1,0,0,0,0,0,1,1,0,0,0,1,1,0,0,0,1,1,0,1,1,0,1,0,1,0,1,1,1,1,1)
# Add info on experimental words
big_it <-c('iena', 'toro', 'cammello', 'agnello', 'pinguino', 'oca','squalo', 'serpente', 
           'prigione', 'panca', 'razzo', 'tenda', 'divano', 'fucile', 'culla', 'bomba' ,
           'meteorite', 'valanga', 'vulcano', 'bombardiere', 'tigre', 'cobra', 'coccodrillo', 'cinghiale',
           'giraffa', 'cavallo', 'delfino', 'cerbiatto', 'scuola', 'quercia', 'contrabbasso', 'cupola')
harm_it <-c('toro', 'iena', 'squalo', 'serpente', 'ape', 'pulce', 'ragno', 'ratto',
            'bomba', 'prigione','razzo', 'fucile', 'bruciatore', 'pugnale', 'ago', 'spina',
            'tigre', 'cobra', 'coccodrillo', 'cinghiale', 'meteorite', 'valanga', 'vulcano','bombardiere',
            'zanzara', 'medusa', 'tarantola', 'zecca', 'mina', 'veleno', 'proiettile', 'coltello')
it_words_2 <- c('tigre', 'cobra', 'coccodrillo', 'cinghiale', 'zanzara', 'medusa', 'tarantola', 'zecca',
                'giraffa', 'cavallo', 'delfino', 'cerbiatto', 'coniglio', 'farfalla', 'scoiattolo', 'passero',
                'meteorite', 'valanga', 'vulcano', 'bombardiere', 'mina', 'veleno', 'proiettile', 'coltello',
                'scuola', 'quercia', 'contrabbasso', 'cupola', 'tazza', 'scarpa', 'cucchiaio', 'mela')

# Add info on experimental factors per word to the dataframe
freq_it$Animate <- ifelse(freq_it$Animate == 1, 'Animate', 'Inanimate')
freq_it$Size <- ifelse(freq_it$Word %in% big_it, 'Big', 'Small')
freq_it$Harm <- ifelse(freq_it$Word %in% harm_it, 'Harmful', 'Harmless')
# Add info on experiment number and convert raw frequencies to frequency per million words
freq_it$Exp <- ifelse(freq_it$Word %in% it_words_2, 2, 1)
freq_it$PerMillion <- freq_it$Freq / 5864.496 #Million words in the corpus

```

Plot frequencies for experiment 1, **Italian**
``` {r PlotFreqIta, message = FALSE, warning = FALSE, echo = FALSE}

# By animacy
it_anim_1 <- ggplot(data = subset(freq_it, Exp == 1), aes(x = Animate, y = PerMillion)) +
  geom_boxplot(aes (fill = Animate), alpha = 0.7) + ylab('Frequency') + xlab('')  + guides(fill = FALSE) +
  geom_text_repel(aes(label = ifelse(Animate == 'Animate' & PerMillion > 10, Word, ''))) +
  scale_fill_brewer(palette="Set1")+
  theme(panel.background = element_rect(fill='white', color = 'black'),
        panel.grid.major = element_line(color = 'grey', linetype = 'dotted'),
        panel.grid.minor = element_line(color = 'grey', linetype = 'dotted'))
# By harmfulness
it_harm_1 <- ggplot(data = subset(freq_it, Exp == 1), aes(x = Harm, y = PerMillion)) +
  geom_boxplot(aes (fill = Harm), alpha = 0.7) + ylab('') + xlab('')  + guides(fill = FALSE) +
  geom_text_repel(aes(label = ifelse(PerMillion > 30, Word, ''))) +
  scale_fill_brewer(palette="Set1")+
  theme(plot.title = element_text(hjust = 0.5))+
  theme(panel.background = element_rect(fill='white', color = 'black'),
        panel.grid.major = element_line(color = 'grey', linetype = 'dotted'),
        panel.grid.minor = element_line(color = 'grey', linetype = 'dotted'))
# By size
it_size_1 <- ggplot(data = subset(freq_it, Exp == 1), aes(x = Size, y = PerMillion)) +
  geom_boxplot(aes (fill = Size), alpha = 0.7) + ylab('') + xlab('')  + guides(fill = FALSE) +
  geom_text_repel(aes(label = ifelse(PerMillion >17, Word, ''))) +
  scale_fill_brewer(palette="Set1")+
  theme(panel.background = element_rect(fill='white', color = 'black'),
        panel.grid.major = element_line(color = 'grey', linetype = 'dotted'),
        panel.grid.minor = element_line(color = 'grey', linetype = 'dotted'))

it_anim_1
it_harm_1
it_size_1
```

Plot word frequency for experiment 2
``` {r PlotFreq2, message = FALSE, warning = FALSE, echo = FALSE}

# By animacy
it_anim_2 <- ggplot(data = subset(freq_it, Exp == 2), aes(x = Animate, y = PerMillion)) +
  geom_boxplot(aes (fill = Animate), alpha = 0.7) + ylab('Frequency') + xlab('')  + guides(fill = FALSE)+
  geom_text_repel(aes(label = ifelse(PerMillion > 30, Word, ''))) +
  scale_fill_brewer(palette="Set1")+
  theme(panel.background = element_rect(fill='white', color = 'black'),
        panel.grid.major = element_line(color = 'grey', linetype = 'dotted'),
        panel.grid.minor = element_line(color = 'grey', linetype = 'dotted'))
# By harmfulness
it_harm_2 <- ggplot(data = subset(freq_it, Exp == 2), aes(x = Harm, y = PerMillion)) +
  geom_boxplot(aes (fill = Harm), alpha = 0.7) + ylab('') + xlab('')  + guides(fill = FALSE)+
  geom_text_repel(aes(label = ifelse(PerMillion > 50 | Harm == 'Harmful' & PerMillion > 10, Word, ''))) +
  scale_fill_brewer(palette="Set1")+
  theme(panel.background = element_rect(fill='white', color = 'black'),
        panel.grid.major = element_line(color = 'grey', linetype = 'dotted'),
        panel.grid.minor = element_line(color = 'grey', linetype = 'dotted'))
# By size
it_size_2 <- ggplot(data = subset(freq_it, Exp == 2), aes(x = Size, y = PerMillion)) +
  geom_boxplot(aes (fill = Size), alpha = 0.7) + ylab('') + xlab('')  + guides(fill = FALSE) +
  geom_text_repel(aes(label = ifelse(PerMillion > 23, Word, ''))) +
  scale_fill_brewer(palette="Set1")+
  theme(panel.background = element_rect(fill='white', color = 'black'),
        panel.grid.major = element_line(color = 'grey', linetype = 'dotted'),
        panel.grid.minor = element_line(color = 'grey', linetype = 'dotted'))

it_anim_2
it_harm_2
it_size_2

```

Run statistical model to check for differences in frequency across experimental factors
``` {r FreqModIT, message = FALSE, warning = FALSE}

# Estimate linear regression model
it_lm1 <- lm(data = subset(freq_it, Exp == 1), PerMillion ~ Animate * Harm * Size)
it_lm2 <- lm(data = subset(freq_it, Exp == 2), PerMillion ~ Animate * Harm * Size)

# Visualize results
Anova(it_lm1)
Anova(it_lm2)

```

### Crosslinguistic differences word-by-word
X and y axis display **proportion of distal demonstratives** (more intuitive)
``` {r LangDiffPlot, message = FALSE, warning = FALSE}

# Experiment 2
Lang_summ <- subset(data_all, !(ExpNr == 1 & Lang == 'IT')) %>% group_by(Lang, ExpNr, NounEng, Animate, Size, Harm, Demonstrative) %>% summarize(count = n()) %>% mutate(PropProximal = count / sum(count))
Lang_summ <- subset(Lang_summ, Demonstrative == 'proximal')

Lang_summ_DK <- subset(Lang_summ, ExpNr == 2 & Lang == 'DK')
Lang_summ_IT <- subset(Lang_summ, ExpNr == 2 & Lang == 'IT')
Lang_summ2 <- cbind(Lang_summ_DK, Lang_summ_IT)[, c(1:9,18)]
colnames(Lang_summ2)[10] <- 'PropProxITA'

p1 <- ggplot(data = subset(Lang_summ2), aes(y = 1 - PropProxITA , x = 1 - PropProximal)) + geom_point(aes(color = Harm, shape = Size)) + geom_smooth(method='lm', color = 'black', size = 0.2,  se = F, linetype = 'dashed') + xlab('Danish') + ylab('Italian') + scale_color_brewer(palette = 'Set1')+
  theme(panel.background = element_rect(fill='white', color = 'black'),
        panel.grid.major = element_line(color = 'grey', linetype = 'dotted'),
        panel.grid.minor = element_line(color = 'grey', linetype = 'dotted'),
        text = element_text(size = 12)) +
  geom_text_repel(aes(label = NounEng))
  
# Same for English
Lang_summ_EN1 <- subset(Lang_summ, ExpNr == 1 & Lang == 'EN')
Lang_summ_DK1 <- subset(Lang_summ, ExpNr == 1 & Lang == 'DK')
Lang_summ1 <- cbind(Lang_summ_DK1, Lang_summ_EN1)[, c(1:9,18)]
colnames(Lang_summ1)[10] <- 'PropProxEN'

p2 <- ggplot(data = subset(Lang_summ1), aes(y = 1 - PropProxEN , x = 1- PropProximal)) + geom_point(aes(color = Harm, shape = Size)) +
  geom_smooth(method='lm', color = 'black', size = 0.2,  se = F, linetype = 'dashed', fullrange = TRUE) + 
  xlab('Danish') + ylab('English')+ scale_color_brewer(palette = 'Set1')+ 
  theme(panel.background = element_rect(fill='white', color = 'black'),
        panel.grid.major = element_line(color = 'grey', linetype = 'dotted'),
        panel.grid.minor = element_line(color = 'grey', linetype = 'dotted'),
        text = element_text(size = 12)) +
  geom_text_repel(aes(label = NounEng))
  
p1
p2

```
